\def\Date{19 Jan 2024}
% \def\FileID{file:}

\documentclass[12pt]{cdblatex}

\begin{document}

% =================================================================================================
% create checkpoint file

\bgroup
\CdbSetup{action=hide}
\begin{cadabra}
   import cdblib
   checkpoint_file = 'tests/semantic/output/geodesic-lsq-midpt.json'
   cdblib.create (checkpoint_file)
   checkpoint = []
\end{cadabra}
\egroup

% =================================================================================================
\section*{Geodesic mid-point for arc-length}

\input{metric.cdbtex}
\input{geodesic-lsq.cdbtex}

This code uses the results of {\tts geodesic-lsq} and {\tts metric} to show that the 2nd and 3rd
order estimates for $L^2_{PQ}$ can be recovered using a mid-point estimate. For the 3rd order estimate
we have
\begin{align*}
   g_{ab}(x) &= \cdb{gab4.601} + \BigO{\eps^4}\\
   L^2_{PQ}  &= \cdb{lsq4.301} + \BigO{\eps^4}
\end{align*}
The code below verifies that
\begin{equation*}
   L^2_{PQ} = g_{ab}(\bar x) Dx^{a} Dx^{b} + \BigO{\eps^4}
\end{equation*}
where $\bar x$ is the \emph{coordinate} midpoint of the geodesic
\begin{equation*}
   {\bar x^a} = \frac{1}{2}\left(x^{a}_{P} + x^{a}_{Q}\right)
\end{equation*}
This result holds true only for the 2nd and 3rd order estimates. Note that the \emph{coordinate} midpoint
is not the \emph{geometric} midpoint of the geodesic.

It might be interesting to see if the higher order estimates could
be recovered by sampling the metric at points other than the mid point.

\clearpage

\begin{cadabra}
   {a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w#}::Indices(position=independent).

   \nabla{#}::Derivative.

   g_{a b}::Metric.
   g^{a b}::InverseMetric.

   R_{a b c d}::RiemannTensor.

   import cdblib

   gab = cdblib.get('g_ab','metric.json')

   lsq2 = cdblib.get('lsq2','geodesic-lsq.json')
   lsq3 = cdblib.get('lsq3','geodesic-lsq.json')
   lsq4 = cdblib.get('lsq4','geodesic-lsq.json')
   lsq5 = cdblib.get('lsq5','geodesic-lsq.json')

   substitute (gab,$x^{a}->(p^{a}+q^{a})/2$)   # evaluate rnc gab at mid-point
   distribute (gab)

   defgab := g_{a b} -> @(gab).

   mid := g_{a b} (q^{a}-p^{a}) (q^{b}-p^{b}).

   substitute     (mid,defgab)
   distribute     (mid)
   sort_product   (mid)
   rename_dummies (mid)
   canonicalise   (mid)

   tst2 := @(lsq2) - @(mid).                             # cdb (tst2.201,tst2)
   tst3 := @(lsq3) - @(mid).                             # cdb (tst3.201,tst3)
   tst4 := @(lsq4) - @(mid).                             # cdb (tst4.201,tst4)
   tst5 := @(lsq5) - @(mid).                             # cdb (tst5.201,tst5)

   substitute     (tst2,$Dx^{a} -> q^{a}-p^{a}$)
   substitute     (tst2,$x^{a} -> p^{a}$)
   distribute     (tst2)
   sort_product   (tst2)
   rename_dummies (tst2)
   canonicalise   (tst2)                                 # cdb (tst2.202,tst2)

   substitute     (tst3,$Dx^{a} -> q^{a}-p^{a}$)
   substitute     (tst3,$x^{a} -> p^{a}$)
   distribute     (tst3)
   sort_product   (tst3)
   rename_dummies (tst3)
   canonicalise   (tst3)                                 # cdb (tst3.202,tst3)

   substitute     (tst4,$Dx^{a} -> q^{a}-p^{a}$)
   substitute     (tst4,$x^{a} -> p^{a}$)
   distribute     (tst4)
   sort_product   (tst4)
   rename_dummies (tst4)
   canonicalise   (tst4)                                 # cdb (tst4.202,tst4)

   substitute     (tst5,$Dx^{a} -> q^{a}-p^{a}$)
   substitute     (tst5,$x^{a} -> p^{a}$)
   distribute     (tst5)
   sort_product   (tst5)
   rename_dummies (tst5)
   canonicalise   (tst5)                                 # cdb (tst5.202,tst5)

\end{cadabra}

\clearpage

% =================================================================================================
\section*{Reformatting}

\begin{cadabra}
   def truncateR (obj,n):

   # I would like to assign different weights to \nabla_{a}, \nabla_{a b}, \nabla_{a b c} etc. but no matter
   # what I do it appears that Cadabra assigns the same weight to all of these regardless of the number of subscripts.
   # It seems that the weight is assigned to the symbol \nabla alone. So I'm forced to use the following substitution trick.

       Q_{a b c d}::Weight(label=numR,value=2).
       Q_{a b c d e}::Weight(label=numR,value=3).
       Q_{a b c d e f}::Weight(label=numR,value=4).
       Q_{a b c d e f g}::Weight(label=numR,value=5).

       tmp := @(obj).

       substitute (tmp, $\nabla_{e f g}{R_{a b c d}} -> Q_{a b c d e f g}$)
       substitute (tmp, $\nabla_{e f}{R_{a b c d}} -> Q_{a b c d e f}$)
       substitute (tmp, $\nabla_{e}{R_{a b c d}} -> Q_{a b c d e}$)
       substitute (tmp, $R_{a b c d} -> Q_{a b c d}$)

       ans = Ex(0)

       for i in range (0,n+1):
          foo := @(tmp).
          bah = Ex("numR = " + str(i))
          keep_weight (foo, bah)
          ans = ans + foo

       substitute (ans, $Q_{a b c d e f g} -> \nabla_{e f g}{R_{a b c d}}$)
       substitute (ans, $Q_{a b c d e f} -> \nabla_{e f}{R_{a b c d}}$)
       substitute (ans, $Q_{a b c d e} -> \nabla_{e}{R_{a b c d}}$)
       substitute (ans, $Q_{a b c d} -> R_{a b c d}$)

       return ans

   tst2 = truncateR (tst2,2)  # cdb (tst2.301,tst2)
   tst3 = truncateR (tst3,3)  # cdb (tst3.301,tst3)
   tst4 = truncateR (tst4,4)  # cdb (tst4.301,tst4)
   tst5 = truncateR (tst5,5)  # cdb (tst5.301,tst5)
\end{cadabra}

\clearpage

% =================================================================================================
\section*{Errors is mid-point estimates for $L^2_{PQ}$}

\begin{dgroup*}
   \begin{dmath*} \left(L^2_{PQ} - g_{ab}(\bar x) Dx^a Dx^b\right)_2 = \cdb{tst2.301} \end{dmath*}
   \begin{dmath*} \left(L^2_{PQ} - g_{ab}(\bar x) Dx^a Dx^b\right)_3 = \cdb{tst3.301} \end{dmath*}
   \begin{dmath*} \left(L^2_{PQ} - g_{ab}(\bar x) Dx^a Dx^b\right)_4 = \cdb{tst4.301} \end{dmath*}
   \begin{dmath*} \left(L^2_{PQ} - g_{ab}(\bar x) Dx^a Dx^b\right)_5 = \cdb{tst5.301} \end{dmath*}
\end{dgroup*}

% =================================================================================================
% export checkpoints in json format

\bgroup
\CdbSetup{action=hide}
\begin{cadabra}
   for i in range( len(checkpoint) ):
      cdblib.put ('check{:03d}'.format(i),checkpoint[i],checkpoint_file)
\end{cadabra}
\egroup

\end{document}

